Programming Language Survey Paper on Haskell

### 2013-04-17 projects/term_paper/paper.tex
Fixed a few errors in the code.
Continued adding code samples.

\subsubsection{Operators and Precedence}
\bi
    \item Operators: postfix notation, naming typically consists of symbols
    \item Functions: infix notation, named using alphanumeric characters in camel case
    \item Any function can be used as an operator by calling it in postfix notation
\begin{minted}{haskell}
f (Int a) => a -> a
f a b = a + b
; invoke the function in postfix notation
print (1 `f` 2)
\end{minted}
    \item Any operator can be called as a function in infix notation
\begin{minted}{haskell}
print ((+) 2 5)
\end{minted}
    \item Operators can be overloaded
\begin{minted}{haskell}
* a b = a * a * b
print (2 * 3)
\end{minted}
\ei

\subsubsection{Selection Constructs}
\bi
    \item Pattern matching
    \item if/then/else
    \item Guards
    \item Case expression
\ei

>>>>

\subsubsection{Operators and Precedence}
\bi
    \item Operators: postfix notation, naming typically consists of symbols
    \item Functions: infix notation, named using alphanumeric characters in camel case
    \item Any function can be used as an operator by calling it in postfix notation
\begin{minted}{haskell}
f :: (Int a) => a -> a -> a
f a b = a + b
; invoke the function in postfix notation
print (1 `f` 2)
\end{minted}
    \item Any operator can be called as a function in infix notation
\begin{minted}{haskell}
print ((+) 2 5)
\end{minted}
    \item Operators can be overloaded
\begin{minted}{haskell}
(*) :: (Num a) => a -> a -> a
(*) a b = a * a * b
print (2 * 3)
\end{minted}
\ei

\subsubsection{Selection Constructs}
\bi
    \item Pattern matching
\begin{minted}{haskell}
favoriteLang :: String -> String
favoriteLang "Haskell" = "You have refined taste, my friend."
favoriteLang "Clojure" = 
    "The wise do not build a house on unsturdy ground."
favoriteLang lang = lang ++ 
    " is a fine choice, but you should give Haskell a spin."
\end{minted}
    \item if/then/else
    \item Guards
\begin{minted}{haskell}
let balance = 200
assessWorth :: Int -> String
assessWorth =
    | balance >= 100000 = "You're rich!"
    | balance >= 100 = "You're rich by student standards!"
    | otherwise = "Need a loan, friend?"
\end{minted}
    \item Case expression
\ei
